Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-11-12 code/analysis_code/analysisscript.Rmd
Referencing done!

#load data. 
```{r}
mydata <- readRDS(data_location)
View(mydata)
```

@@

>>>>

#load data. 
```{r}
mydata <- readRDS(data_location)
```

#outcome split
```{r}
mydata$infection_status_info %>% table()
```

@@

#we want to predict each infection status level, not a single contrast. It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()

#make a recipe

```{r}
mydata_recipe <- 
  recipe(infection_status_info ~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure, data = mydata)
```

#make a model
#choose multinom_reg() + nnet
```{r}
mydata_model <- 
  multinom_reg() %>% 
  set_engine("nnet")
```

#resampling method
```{r}
set.seed(200)
mydata_folds <- vfold_cv(mydata, v = 10)
```

#make workflow
```{r}
mydata_wf <- 
  workflow() %>% 
  add_model(mydata_model) %>% 
  add_recipe(mydata_recipe)
```

#fit
```{r}
mydata_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds)
```

#metrics
```{r}
collect_metrics(mydata_fit)
```

### 2021-11-12 code/analysis_code/more.Rmd
Referencing done!

---
title: "analysis"
author: "Ehsan"
date: "10/27/2021"
output: html_document
---

```{r}
library(tidymodels)
library(readr)       # for importing data
library(tidyverse)
library(dotwhisker)
library(broom.mixed)
library(table1)
library(here)
```

@@

#load data. 
```{r}
mydata <- readRDS(data_location)
```

@@

#get a table
```{r}
overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
overall_summary
```
```{r}
df100 = data.frame(overall_summary)
summarytable_file = here("results", "Overall.rds")
saveRDS(df100, file = summarytable_file)
```

#The main "outcome variable" is the knowledge of infection status (positive/negative/not tested). There are "predisposing factors" (age, sex, education level, chronic disease history etc), "enabling factors" (socio-economic status, area of residence, source of covid news etc) and "need for care factors" (level of fear of reinfection, quarantined or not). We'll do logistic regression analysis for key factors of epredisposing, enabling and need for care factors.

#We'll start with logistic regression model betweem infection status and Age, Sex, Education level (Key Predisposing Factors)
```{r}
lg_mod <- 
       logistic_reg() %>% 
       set_engine("glm")
lg_fit <-
       lg_mod %>%
       fit(infection_status_info ~ Age + Sex + education, data = mydata)
lg_fit
```

```{r}
tidy(lg_fit)
```

```{r}
lg_fit_table_predisposing <- tidy(lg_fit)
```

# saved it as a file
```{r}
summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
```

```{r}
glance(lg_fit)
```

```{r}
lg_fit_statistics_predisposing <- glance(lg_fit)
```

# saved it as a file
```{r}
summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
```

#Then, we'll do log model betweem infection status and socio economic status, area of residence,student/healthworker, source of covid news (Key enabling Factors)
```{r}
lg_fit1 <-
       lg_mod %>%
       fit(infection_status_info ~ economic_status + residence + trusted_source , data = mydata)
lg_fit1
```

```{r}
tidy(lg_fit1)
```

```{r}
lg_fit_table_enabling <- tidy(lg_fit1)
```

# saved it as a file
```{r}
summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
saveRDS(lg_fit_table_enabling, file = summarytable_file14)
```

```{r}
glance(lg_fit1)
```

```{r}
lg_fit_statistics_enabling <- glance(lg_fit1)
```

# saved it as a file
```{r}
summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
```

#Then, we'll do log model betweem infection status and level of fear of infection and quarantined or not (Key need for care factors )
```{r}
lg_fit2 <-
       lg_mod %>%
       fit(infection_status_info ~ quarantined_or_not + worry_level , data = mydata)
lg_fit2
```

```{r}
tidy(lg_fit2)
```

```{r}
lg_fit_table_needforcare <- tidy(lg_fit2)
```

# saved it as a file
```{r}
summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
```

```{r}
glance(lg_fit2)
```

```{r}
lg_fit_statistics_needforcare <- glance(lg_fit2)
```

# saved it as a file
```{r}
summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
```

#compare three models
```{r}
compare_log_model <- anova(lg_fit$fit, lg_fit1$fit, lg_fit2$fit)
compare_log_model
```

#we want to predict each infection status level, not a single contrast. It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()

>>>>

---
---
title: "analysis"
author: "Ehsan"
date: "10/27/2021"
output: html_document
---

```{r}
library(tidymodels)
library(readr)       # for importing data
library(tidyverse)
library(dotwhisker)
library(broom)
library(table1)
library(here)
library(nnet)
library(patchwork)
library(knitr)
library(GGally)
library(pacman)
library(dplyr)
```

@@

#load data. 
```{r}
mydata <- readRDS(data_location)
View(mydata)
```

@@

### 2021-11-12 code/processing_code/processingscript.Rmd
Referencing done!

```{r}
processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student_or_heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = `Which of the following categories best describes your current socio-economic situation?`,
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = `Are you currently working/studying from home because of the COVID-19 outbreak?`,
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,
                               "chronic_disease_history" = `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`,
                              "social_distance_practice" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`,
                              "follow_preventive_measure" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```

>>>>

```{r}
processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                                      "serial" = `Serial number`,
                               "student_or_heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = `Which of the following categories best describes your current socio-economic situation?`,
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = `Are you currently working/studying from home because of the COVID-19 outbreak?`,
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,
                               "chronic_disease_history" = `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`,
                              "social_distance_practice" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`,
                              "follow_preventive_measure" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```

### 2021-11-12 products/manuscript/Manuscript.Rmd
Referencing done!

@@

_**Measures**_
Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

@@

_**Enabling factors**_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.

@@

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

This paper [@Leek2015a] discusses types of analyses.

>>>>

Testing can help people determine if they are infected with SARS-CoV-2 – regardless of whether they have symptoms – and whether they are at risk of spreading the infection to others. Testing of all people for SARS-CoV-2, including those who have no symptoms, who show symptoms of infection, and who may have been exposed to the virus can help prevent the spread of COVID-19 and identify people in need of care in a timely fashion. A positive test early in the course of the illness enables individuals to isolate themselves – reducing the chances of infecting others and allowing them to seek treatment earlier, likely reducing disease severity and the risk of long-term disability, or death.

A negative test does not mean the person will not be able to acquire and transmit the infection in the future. Therefore, even if an individual is test negative, continuation of hygiene practices to self-protect and others by washing hands with soaps/ sanitizers frequently, physical distancing, and wearing a face mask is required. A positive test means isolation is mandatory, and that others with whom the individual may have been in contact since the time of exposure should also get tested. Since it is recognized that nearly half of all SARS-CoV-2 infections are transmitted by pre-symptomatic and asymptomatic people, identifying infected individuals while they are pre-symptomatic, as well as those who are asymptomatic, will play a major role in containing the pandemic.

Scanty research has been conducted to identify factors associated with the uptake of COVID-19 testing. In a cross-sectional community survey in Ontario, Canada, 3.3% tested positive for SARS-CoV-2. The odds of being tested increased with age, male sex, several underlying health conditions, previous use of health care services, and higher household income [@SundaramE]. Comparing the odds of COVID-19 positive diagnosis with test-negatives and untested individuals, older age, certain comorbidities, such as hypertension, diabetes and heart diseases, higher previous use of health care services were associated with increased odds of a positive SARS-CoV-2 test result [@SundaramE]. Using UK biobank data, being tested for COVID-19 was associated with male sex, Black ethnicity, lower socioeconomic status, occupation (being a health care worker, retired, unemployed), ever smoker, comorbidities, and exposure to particulate matter (PM) 2.5 absorbance [@Chadeau-hyam]. Among tested individuals, only male sex, non-White ethnicity, and lower education and none of the comorbidities or health risk factors were associated with a COVID-19 positive diagnosis [Chadeau-Hyam]. Workers in the healthcare sector are also at a higher risk of testing positive. A meta-analytic study showed that the pooled prevalence of healthcare workers testing positive for COVID-19 was between 7 to 11% [@Gomez-Ochoa].

@@

_**Measures**_
Using Andersen’s model of health care utilization , study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

@@

_**Enabling factors**_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel[@Bono].

@@
